EpisoPass: Password Management based on \\ Episodic Memories

### 2016-04-13 paper/UIST2016/paper.tex
...

We propose a password manager \textit{EpisoPass} that supports
generating strong passwords based on the user's secret and unforgettable
episodic memories.
%
To use EpisoPass,
a user first collects question-answer pairs related to his episodic memory
and registers them with many fake answers.
%
When a user wants to generate a password,
EpisoPass shows the questions and lists of possible answers and asks
the user to select correct ones.
Then EpisoPass generates a password by substituting characters of the
seed string based on the answer selections.
%
If only the user knows the correct answer,
% If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without using master passwords or secret devices that are
usually required on conventional password managers.
%
\end{abstract}

@@

Character substitution is performed based on the hash value
calculated from concatinating all the selected answers.
For example, if the user selects ``\texttt{Ebisawa}'' to the question ``\texttt{Who's the bully?}'',
a hash value calculated from  ``\texttt{Who's the bully:Ebisawa}''
is used for the substitution.
Details of the algorithm is shown in the Appendix.

@@

\subsection{Simple implementation}
%   実装が簡単

@@

    %たとえばハッシュ値$M$が$12345678...$だったとき、1桁目を計算する$f()$についてはN=0x1234となる。
    If the hash value $M$ is $12345678...$,
    $f_{\texttt{\scriptsize 0x1234}}$ is used as the substitution function for the first character,
    $f_{\texttt{\scriptsize 0x5678}}$ is used as the substitution function for the second character, etc.
\end{enumerate}

>>>>

We propose a password manager \textit{EpisoPass} that supports
generating strong passwords based on the user's secret and unforgettable
episodic memories.
%
To use EpisoPass,
a user first collects question-answer pairs related to his episodic memory
and registers them with fake answers.
%
When a user wants to generate a password,
EpisoPass shows the questions and lists of possible answers and asks
the user to select correct ones.
Then EpisoPass generates a password by substituting characters of the
seed string based on the answer selections.
%
If only the user knows the correct answer,
% If the right answers to the questions are known only to the user,
the password cannot be guessable by other people, and
various strong passwords can be easily managed
without using master passwords or secret devices that are
usually required on conventional password managers.
%
\end{abstract}

@@

Character substitution is performed based on the hash value
calculated from concatinating all the selected answers.
For example, if the user selects ``\textbf{\texttt{Ebisawa}}'' to the question ``\textbf{\texttt{Who's the bully?}}'',
a hash value calculated from  ``\textbf{\texttt{Who's the bully:Ebisawa}}''
is used for the substitution.
Details of the algorithm is shown in the Appendix.

@@

\subsection{Simplicity}

@@

    %たとえばハッシュ値$M$が$12345678...$だったとき、1桁目を計算する$f()$についてはN=0x1234となる。
    If the hash value $M$ is $12345678...$,
    $f_{\textbf{\texttt{\scriptsize 0x1234}}}$ is used as the substitution function for the first character,
    $f_{\textbf{\texttt{\scriptsize 0x5678}}}$ is used as the substitution function for the second character, etc.
\end{enumerate}
